\problemname{Springoalla}
Springoalla loves to run.
She knows of $n$ running trails, and for each of them she knows exactly how long it takes her to run the trail and then back again.
The first time she runs a new trail, she familiarizes herself with it.
More specifically, she learns where the half-way point of the trail is, and can from then on turn back after half the trail.
That halves her running time.
For example, she can run half of a $20$ minute trail in $10$ minutes, but only after first having run the entire trail once.

Springoalla wants to run for at least $t$ minutes without running for too long.
Given the time it takes to run each trail, compute the minimum number of minutes $t_s \ge t$ she must run.
If there are several ways to run $t_s$ minutes, she wants to make as few runs $n_s$ as possible, where every time she sets off from the starting point counts as one run, whether she runs a whole or a half trail.

\section*{Input}
The first line of input contains the integers $n$ and $t$ ($1 \le n \le 1000$, $1 \le t \le 10^5$), the number of trails and the time Springoalla wants to run.
Note that $t$ is not necessarily even.

The second line contains $n$ integers $l_i$, where $2 \le l_i \le 40{,}000$ is an even integer: the number of minutes it takes to run trail $i$.

\section*{Output}
First output the integers $t_s$ and $n_s$, the time Springoalla must run and the total number of runs she makes.
Then output $n$ integers, where the $i$th is the number of minutes she should spend on trail $i$.
If there are several solutions with the same $t_s$ and $n_s$ you may output any one of them.


\section*{Scoring}
Your solution will be tested on a set of test groups.
To earn points for a group, you must pass all test cases in that group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Points} & \textbf{Constraints} \\ \hline
  $1$    & $20$        & $n \le 10, t \le 1000$ \\ \hline
  $2$    & $30$        & Springoalla only needs to run whole trails. \\ \hline
  $3$    & $50$        & No additional constraints. \\ \hline 
\end{tabular}
