\problemname{Number Words}

Monika writes down all Swedish number words between 1 and $N$. She then sorts the words alphabetically and concatenates them into a single long string. Write a program that finds letter number $K$, $K+1$, and $K+2$ in Monika's string.

To avoid problems with character encoding we replace å and ä with a. Furthermore, we use the forms etthundra, ettusen (note the spelling), enmiljon, and enmiljard, but only when the digit 1 stands \emph{alone} before the magnitude word (not counting earlier magnitude words). When the digit 1 instead is at the end of a prefix denoting \emph{several} thousands, millions, or billions, we always write ``en'' for simplicity: tjugoentusen, etthundraenmiljoner, tvahundraattioenmiljarder, etc. At the very end of a number word, we always write the digit 1 as ``ett''.

A table with the basic number words and some examples of longer words hopefully clarifies the rules:

\begin{tabular}{|r|l||r|l|} \hline
{\bf Number} & {\bf Number word} & {\bf Number} & {\bf Number word} \\ \hline
1 & ett & 10 & tio\\
2 & tva & 20 & tjugo\\
3 & tre & 30 & trettio\\
4 & fyra & 40 & fyrtio\\
5 & fem & 50 & femtio\\
6 & sex & 60 & sextio\\
7 & sju & 70 & sjuttio\\
8 & atta & 80 & attio\\
9 & nio & 90 & nittio\\
11 & elva & 100 & etthundra\\
12 & tolv & 198 & etthundranittioatta\\
13 & tretton & 201 & tvahundraett\\
14 & fjorton & 1121 & ettusenetthundratjugoett\\
15 & femton & $581\,743$ & femhundraattioentusensjuhundrafyrtiotre \\
16 & sexton & $51\,101\,001$ & femtioenmiljoneretthundraentusenett\\
17 & sjutton & $162\,500\,020$ & etthundrasextiotvamiljonerfemhundratusentjugo\\
18 & arton & $1\,002\,001\,004$ & enmiljardtvamiljonerettusenfyra\\
19 & nitton & $91\,011\,091\,000$ & nittioenmiljarderelvamiljonernittioentusen\\ \hline
\end{tabular}

And as an additional check, we give the length of Monika's string for some different $N$:

\begin{tabular}{|r|r|}\hline
{\bf N} & {\bf String length} \\ \hline
999 & 16260 \\
9999 & 235600 \\
99999 & 2908000 \\
999999 & 37425000 \\
9999999   & 472250000 \\
99999999 & 5319500000\\
999999999 & 61585000000\\
9999999999 & 722850000000 \\
99999999999 &	7834500000000 \\
999999999999 &86744000000000 \\ \hline
\end{tabular}


\section*{Input}
A line with two integers $N$ and $K$, where $1 \leq N < 10^{12}$ and $1 \leq K \leq L-2$, where $L$ is the length of the formed string.

\section*{Output}
A line with three letters without separating spaces: letter number $K$, $K+1$, and $K+2$ in the string. 

\section*{Scoring}
Your solution will be tested on a set of test groups.
To earn points for a group, you must pass all test cases in that group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Points} & \textbf{Constraints} \\ \hline
  $1$   & $15$       & $N \leq 2000 $\\ \hline
  $2$   & $20$       & $N \leq 5*10^5 $\\ \hline
  $3$   & $30$       & $N = 999\,999\,999\,999 $\\ \hline
  $4$   & $35$       & No additional constraints. \\ \hline
\end{tabular}

\section*{Explanation of the First Example}

Monika's string, written with 40 characters per line, is

\begin{verbatim}
artonattaelvaettfemfemtonfjortonfyranion
ittonsexsextonsjusjuttontiotjugotjugoett
tjugofemtjugofyratjugosextjugotretjugotv
atolvtretrettontva
\end{verbatim}
